---
title: "Lab_hw09"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

# Activity 9 Problem 1
```{r}
odd_count = function(x) {
    odd_num = 0
    for (i in 1:length(x)) {
        if (x[i] %% 2 == 1) 
        odd_num = odd_num + 1 
        }
    return(odd_num) 
}
odd_count2 = function(x) {
    sum(ifelse(x %% 2 == 0, 0, 1))
}


x <- seq(1:100000)
microbenchmark(odd_count(x), odd_count2(x))
```

## Q1: Microbenchmark 
```{r}
library(microbenchmark)
col_sum1 = function(x) {
    colSum = rep(NA, ncol(x))
    for (i in ncol(x)) {
        colSum[i] = sum(x[, i])
    }
    colSum
}

col_sum2 = function(x) {
    apply(x, 2, sum)
}

col_sum3 = function(x) {
    colSums(x)
}

x <- matrix(1:90000, nrow = 300, ncol = 300, byrow = TRUE)
microbenchmark(col_sum1(x), col_sum2(x), col_sum3(x))
```

## Q2: Modify the sorting function (sort_vec) from “Assignment 8” (problem 3) so that it should take an additional argument ascending which causes sorting in increasing order when ‘ascending = TRUE’. 
```{r}
sort_vec = function(x, ascending = TRUE) {
if (length(x) < 2) return(x)
for (last in length(x):2) { 
    for (first in 1:(last - 1)) {
            if (ascending == TRUE) {
                if (x[first] > x[first + 1]) { 
                    temp = x[first]
                    x[first] = x[first + 1] 
                    x[first + 1] = temp
                } 
            }else {
            if (x[first] < x[first + 1]) { 
            temp = x[first]
            x[first] = x[first + 1] 
            x[first + 1] = temp
        }  
        }
    }
}
x
}
x <- c(3, 1, 2)
sort_vec(x, ascending = TRUE)
sort_vec(x, ascending = FALSE)
```

## Q3: Consider a simple random walk with starting point 0 and a step -1 or 1. Below is the code with dynamically allocated memory. Write your code with preallocated memory and compare time for both versions using system.time() function (use N = 1000, 10000 and 1000000).
```{r}
N = 1000
#N = 10000
#N = 1000000
data_series = 0 
system.time({
    for (i in 2:N){
        data_series[i] = data_series[i-1] + sample(c(-1, 1), 1) }
})

system.time({
   data_series =  rep(0, N)
    for (i in 2:N){
        data_series[i] = data_series[i-1] + sample(c(-1, 1), 1) }
})
```

